---
title: "Gaurav_Titanic_Final"
output: html_document
---

```{r include=FALSE}
library(dygraphs)
library(dplyr)
library(data.table)
library(zoo)
library(forecast)
library(ggplot2)
library(scales)
library(splines)
library(sqldf)
library(reshape2)
library(pystr)
library(psych)
library(plyr)
library(PerformanceAnalytics)
library(MASS)
library(lattice)
library(gridExtra)
library(grid)
library(graphics)
library(ggplot2)
library(randomForest)
library(caret)
library(rpart.plot)
library(rpart)
library(party)
library(aemo)
library(datasets)
library(dplyr)
library(scales)
library(tcltk)
library(lubridate)
library(forecast)
library(reshape)
library(forecast)
library(reshape)
library(RColorBrewer)
library(rpart.plot)
library(rattle)

```


Import the data set i.e train and test
```{r}
test <- read.csv("D:/Multivariate/Titanic/test.csv")
train <- read.csv("D:/Multivariate/Titanic/train.csv")
#combine the train and test data sets into a single data set 
test$Survived <- NA
FullData <- rbind(train, test)
```
Now parse the Name feature
```{r}
# Convert to a string
FullData$Name <- as.character(FullData$Name)

#bring out the title from the name
FullData$Title <- sapply(FullData$Name, FUN=function(x) {strsplit(x, split='[,.]')[[1]][2]})
FullData$Title <- sub(' ', '', FullData$Title)

table(FullData$Title)

#there are many titles which are rare so replace them with the median of the group title
FullData$Title[FullData$Title %in% c('Mme', 'Mlle')] <- 'Mlle'
FullData$Title[FullData$Title %in% c('Capt', 'Don', 'Major', 'Sir')] <- 'Sir'
FullData$Title[FullData$Title %in% c('Dona', 'Lady', 'the Countess', 'Jonkheer')] <- 'Lady'

table(FullData$Title)
# Convert title to a factor
FullData$Title <- factor(FullData$Title)

# Engineered variable: Family size
FullData$SizeOfFamily <- FullData$SibSp + FullData$Parch + 1

```

Fill NA with the mean of the age
```{r}
summary(FullData$Age)
FullData$Age[which(is.na(FullData$Age))] <- mean(FullData$Age,na.rm = TRUE)

#fill NA with the mean of the Fare
FullData$Fare <- mean(FullData$Fare, na.rm = TRUE)
summary(FullData$Embarked)
which(FullData$Embarked == '')
FullData$Embarked[c(62,830)] = "S"
FullData$Embarked <- factor(FullData$Embarked)
```

Separte train and the test data
Divide the T_tain data into two parts so that it can be used as the validation data in the prediction
```{r}
T_train <- FullData[1:600,]
T_test <- FullData[892:1309,]
valid_data <- FullData[600:891,]
```

Using random forest
```{r}

randomforest_model <- randomForest(as.factor(Survived) ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title + SizeOfFamily,
                      data=T_train, 
                      importance=TRUE, 
                      ntree=453)
#predict validate survival
rf_predict_valid <- predict(randomforest_model, valid_data)
confusionMatrix(rf_predict_valid, valid_data$Survived)

rf_predict_test <- predict(randomforest_model, T_test)
rf_write_test <- data.frame(PassengerId = T_test$PassengerId, Survived = rf_predict_test)
write.csv(rf_write_test, file = "rf_prediction.csv", row.names = FALSE)

```

Model Condtional Tree Ctree
```{r}
ctree_model <- ctree(as.factor(Survived) ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title + SizeOfFamily,
               data = T_train)
```
check the accuracy of the model on validate data
```{r}
ctree_predict_valid <- predict(ctree_model, valid_data)
confusionMatrix(ctree_predict_valid, valid_data$Survived)
```
predict the Survival of test data
```{r}
ctree_predict_test <- predict(ctree_model, T_test)
write_ctree_test <- data.frame(PassengerId = T_test$PassengerId, Survived = ctree_predict_test)
write.csv(write_ctree_test, file = "ctree_predict.csv", row.names = FALSE)
```


build model for cforest using T_train
using cforest tree classification model
```{r}
set.seed(415)
cforest_model <- cforest(as.factor(Survived) ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title + SizeOfFamily,
               data = T_train, controls=cforest_unbiased(ntree=2400, mtry=3))
```
for testing purpose check the accuracy of the model on validate data
```{r}
predict_valid <- predict(cforest_model, valid_data, OOB=TRUE, type = "response")
confusionMatrix(predict_valid, valid_data$Survived)
```

Now predict the test data and write it in a .csv file
```{r}
predict_test <- predict(cforest_model, T_test, OOB=TRUE, type = "response")
write_cforest_test <- data.frame(PassengerId = T_test$PassengerId, Survived = predict_test)
write.csv(write_cforest_test, file = "cforest_prediction.csv", row.names = FALSE)
```
